\documentclass[aps,prd,showpacs,showkeys,notitlepage,preprintnumbers,nofootinbib]{revtex4-1}
\usepackage{amsmath,amssymb,amsthm,bm,color,hyperref,blindtext,fullpage}
\usepackage{graphics,subfigure,rotating,etoolbox,amsbsy,graphicx}
\usepackage[utf8]{inputenc}
\usepackage[toc,page]{appendix}
\usepackage[dvipsnames]{xcolor}
\usepackage{float} %To use H as position
\def\cred{\color{red}}
\def\cgreen{\color{green}}
\newcommand{\todo}[1]{{\cred todo: #1}}
\newcommand{\eq}[1]{Eq.~(\ref{#1})}
\newcommand{\Eq}[1]{Eq.~(\ref{#1})}
\newcommand{\sect}[1]{section~\ref{#1}}
\newcommand{\sects}[1]{sections~\ref{#1}}
\newcommand{\App}[1]{appendix~\ref{#1}}
\newcommand{\fig}[1]{figure~\ref{#1}}
\newcommand{\figs}[1]{figures~\ref{#1}}
\newcommand{\tab}[1]{table~\ref{#1}}
\newcommand{\tabs}[1]{tables~\ref{#1}}
\newcommand{\tr}{\mbox{Tr}}
\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup}
\setlength{\tabcolsep}{10pt}

\begin{document} 

\title{Neutron electric dipole polarizability}


\author{Michael Engelhardt}
\email{engel@nmsu.edu}
\affiliation{Department of Physics, New Mexico State University,
Las Cruces, NM 88003, USA}
\author{Roman H\"ollwieser}
\email{hoellwieser@uni-wuppertal.de}
\affiliation{Department of Physics, University of Wuppertal,
42119 Wuppertal, Germany}
\affiliation{Department of Physics, New Mexico State University,
Las Cruces, NM 88003, USA}
\author{Jesus Saenz}
\email{jmsaenzv@nmsu.edu}
\affiliation{Institute of Engineering and Technology,
Universidad Aut\'onoma de Ciudad Ju\'arez, 32310, Ciudad Ju\'arez, Mexico}
\affiliation{Department of Physics, New Mexico State University,
Las Cruces, NM 88003, USA}

% \date{\today}

\begin{abstract}
We revisit the neutron electric dipole polarizability and present results from a lattice calculation using the background method with increased statistics, taking into account connected as well as disconnected contributions.  
We further subtract the point-like contribution determined from a Foldy-Wouthuysen transformation in a preceding work. 
\end{abstract}

% \pacs{11.15.Ha, 12.38.Gc}
% not sure we need these anymore

\keywords{Neutron polarizabilities, neutron electric dipole polarizability, lattice QCD}

\maketitle

% \tableofcontents

% \newpage

\section{Introduction}
\label{introsec}
\input{intro.tex}

\section{Calculation method}
\input{method.tex}

\section{Measurement Results}
\subsection{Quark renormalization}
\input{quarkrenorm.tex}
\subsection{Foldy-Wouthuysen contribution to $\alpha_E$ at $m_\pi$= 357 MeV.}
\input{foldy}
\subsection{Neutron mass shift}
\subsubsection{Numerical measurements}
\input{numMeasurements.tex}
\input{mpi357-3windowConnected.tex}
\input{mpi357-1windowConnected.tex}
\input{mpi357-3windowAll.tex}
\input{mpi357-1windowAll.tex}

\section{Retardation effects}
\label{retardation}
\input{retardation.tex}

\section{Conclusions}
\input{conclusio.tex}


\section*{Acknowledgments}
Fruitful discussions with S.~A.~Coon, W.~Detmold, H.~Grie\ss hammer and B.~Pasquini are acknowledged.
This research was supported by the Erwin Schr\"odinger Fellowship program of the Austrian Science Fund FWF (``Fonds zur F\"orderung der wissenschaftlichen Forschung'') under Contract No. J3425-N27 (R.H.) and the U.S.~Department of Energy, Office of Science, Office of Nuclear Physics through grant DE-FG02-96ER40965 (M.E.,J.S.).



\bibliographystyle{utphys} % We choose the &quot;plain&quot; reference style
\bibliography{main}

\end{document}


\section*{References}
\begin{thebibliography}{99}
\bibitem{babusci} D.~Babusci, G.~Giordano, A.~I.~L'avov, G.~Matone, A.~M.~ Nathan, Phys.~Rev.~C {\bf{58}}, 1013,1041 (1998), arXiv: hep-ph/9803347.
\bibitem{hagelstein} F.~Hagelstein, Symm.~ {\bf{12}}, 1407 (2020).
\bibitem{levchuk} M.~I.~ Levchuk, A.~I.~L'vov, Nucl.~Phys.~{\bf{A674}}, 449 (2020).
\bibitem{bernard1} V.~Bernard, N.~Kaiser, U.~Meissner, Phys.~Rev.~Lett.~ {\bf{67}}, 1515 (1991).
\bibitem{bernard2} V.~Bernard, N.~Kaiser, U.~Meissner, Nucl.~Phys.~{\bf{B373}}, (1992)
\bibitem{detmold} W.~Detmold, B.~C.~Tiburzi, A.~Walker-Loud, Phys. Rev. D {\bf{73}}, 114505 (2006).
\bibitem{schumacher} M.~Schumacher, LHEP {\bf{2}}, 4 (2019).
\bibitem{foldywouthuysen} J.~Saenz, M.~Engelhardt, R.~H\"ollwieser,
Phys. Rev. D. {\bf 104}, 056002 (2021).
\bibitem{holstein} B.~Holstein, D.~Drechsel, B.~Pasquini, and M.~Vanderhaeghen, Phys.~Rev.~C {\bf{61}}, 034316 (2000).
\bibitem{drechsel} D.~Dreschsel, B.~Pasquini, and M.~Vanderhaeghen, Phys.~Rep.~{\bf{378}}, 99 (2003).
\bibitem{hildebrandt} R.~Hildebrandt, H.~Grie{\ss}hammer, T.~Hemmert, and B.~Pasquini, Eur.~Phys.~J.~ A {\bf{20}}, 293 (2004).
\bibitem{schumacher2} M.~Schumacher, Porg.~Part.~Nucl.~Phys.~{\bf{55}}, 567 (2005).
\bibitem{pasquini1} B.~Pasquini, D.~Drechsel, and M.~Vanderhaeghen, Phys.~Rev.~C {\bf{76}}, 015203 (2007).
\bibitem{pasquini2} B.~Pasquini, P.~Pedroni, adn D.~Drechsel, Phys.~Lett.~ B {\bf{687}}, 160 (2010).
\bibitem{griesshammer2} H.~Grie{\ss}hammer, J.~McGovern, D.~R.~Phillips, and G.~Feldman, Prog.~Part.~Nucl.~Phys.~{\bf{67}}, 841 (2012).
\bibitem{mcgovern} J.~McGovern, D.~R.~Phillips, and H.~Grie{\ss}hammer, Eur.~Phys.~J.~A {\bf{49}}, 12 (2013).
\bibitem{holstein2} B.~Holstein adn S.~Scherer, Annu.~Rev.~Nucl.~Part.~Sci.~{\bf{64}}, 51 (2014).
\bibitem{myers} L.~S.~Myers {\it{et al.}} (COMPTON@MAX-lab Collaboration), Phys.~Rev.~Lett.~{\bf{113}}, 262506 (2014).
\bibitem{martel} P.~Martel {\it{et al.}} (A2 Collaboration), Phys.~Rev.~Lett.~{\bf{114}}, 112501 (2015).
\bibitem{gryniuk} O.~Gryniuk, F.Hagelstein, and V.~Pascalutsa, Phys.~Rev.~D {\bf{92}}, 074031 (2015).
\bibitem{gryniuk2} O.~Gryniuk, F.~Hagelstein, abd V.~Pascalutsa, Phys.~Rev.~D {\bf{94}}, 034043 (2016).
\bibitem{hagelstein2} F.Hagelstein, R.~Miskimen, and V.~Pascalutsa, Prog.~Part.~Nucl.~Phys.~{\bf{88}}, 29 (2016).
\bibitem{griesshammer3} H.~Grie{\ss}hammer, J.~McGovern, and D.R.~Phillips, Eur.~Phys.~J.~A {\bf{54}}, 37 (2018).
\bibitem{pasquini3} B.~Pasquini, P.~Pedroni, and S.~Sconfietti, Phys.~Rev.~C {\bf{98}}, 015204 (2018).
\bibitem{pasquini4} B.~Pasquini and M.~Vanderhaeghen, Annu.~Rev.~Nucl.~Part.~Sci.~{\bf{68}}, 75 (2018).
\bibitem{pasquini5} B.~Pasquini, P.~Pedroni, and S.~Sconfietti, J.~Phys.~G {\bf{46}}, 104001 (2019).
\bibitem{miskimen} R.~Miskimen, Proc.~Sci., CD2018 ({\bf{2019}}) 015.
\bibitem{martel2} P.~Martel {\it{et al.}} (A2 Collaboration), Porc.~Sic., CD2018 ({\bf{2019}}) 038.
\bibitem{paudyal} D.~Paudyal {\it{et al.}} (A2 Collaboration), Phys.~Rev.~C {\bf{102}}, 035205 (2020).
\bibitem{melendez} J.~Melendez, R.~Furnstahl, H.~Grie{\ss}hammer, J.~McGovern, D.~R.~Phillips, and M.~Patrola, Eur.~Phys.~J.~A {\bf{57}}, 81 (2021).

\bibitem{fiebig} H.~Fiebig, W.~Wilcox, R.~M.~Woloshyn, Nucl. Phys. {\bf{B324}}, 47 (1989).
\bibitem{christensen2} J.~Christensen, W.~Wilcox, F.~X.~Lee, K.~Zhou, Phys. Rev. {\bf{72}}, 034503 (2005).
\bibitem{lee} F.~X.~Lee, L.~Zhouz, W.Wilcox, J.~Christensen, Phys. Rev D{\bf{73}},  034503 (2006).
\bibitem{shintani} E.~Shintani, S.~Aoki, N.~Ishizuka, K.~Kanaya, Y. Kikukawa, Y.~Kuramashi,
M.~Okawa, A.~Ukawa, and T.~Yoshie, Phys.~Rev.~D {\bf{75}}, 034507 (2007).
\bibitem{engelhardt1} M.~Engelhardt, Phys. Rev. D {\bf{76}}, 114502 (2007).
\bibitem{engelhardt2} M.~Engelhardt, Proc. Sci. LAT2009 ({\bf{2009}}) 128.
\bibitem{detmold2} W.~Detmold, B.~Tiburzi, and A.~Walker-Loud, Phys.~Rev.~D {\bf{79}}, 094505 (2009).
\bibitem{detmold3} W.~Detmodl, B.~Tiburzi, and A.~Walker-Loud, Phys.~Rev.~D {\bf{81}}, 054502 (2010).
\bibitem{engelhardt3} M.~Engelhardt, Proc. Sci. Lattice 2011 ({\bf{2011}}) 153.
\bibitem{alexandru} A.~Alexandru and F.~X.~Lee, Proc. Sci. LAT2009 ({\bf{2009}}) 144.
\bibitem{lee1} F.~X.~ Lee and A. Alexandru, Proc.~Sci., Lattice 2010 ({\bf{2010}}) 148.
\bibitem{lee3} F.~X.~ Lee and A.~Alexandru, Proc.~Sci., Lattice 2011 ({\bf{2011}}) 317.
\bibitem{lujan} M.~Lujan, A.~Alexandru, W.~Freeman, and F.~X.~Lee, Phys.~Rev.~D {\bf{89}}, 074506 (2014).
\bibitem{freeman} W.~Freeman, A.~Alexandru, M.~Lujan, adn F.~X.~Lee, Phys.~Rev.~D {\bf{90}}, 054507 (2014).
\bibitem{luschevskaya} E.~V.~Luschevskaya, O.~E.~Solovjeva, O.~A.~Kochetkov, and O.~V.~Teryaev, Nucl.~Phys.~{\bf{B898}},
627 (2015).
\bibitem{lujan2} M.~Lujan, A.~Alexandru, W.~Freeman, and F.~X.~Lee, Phys.~Rev.~D {\bf{94}}, 074506 (2016).
\bibitem{primer} T.~Primer, W.~Kamleh, D.~Leinweber, and M.~Burkardt, Phys.~Rev.~D {\bf{89}}, 034508 (2014).
\bibitem{bignell} R.~Bignell, J.~Hall, W.~Kamleh, D.~Leinweber, and M.~Burkardt, Phys.~Rev.~D {\bf{98}}, 034504 (2018).
\bibitem{bignell2} R.~Bignell, W.~Kamleh, and D.~Leinweber, Phys.~Rev.~D {\bf{101}}, 094502 (2020).
\bibitem{bignell3} R.~Bignell, W.~Kamleh, adn D.~Leinweber, Phys.~Lett.~B {\bf{811}}, 135853 (2020).
\bibitem{he} F.~He, D.~Leinweber, A.~Thomas, adn P.~Wang, Phys.~Rev.~D {\bf{102}}, 114509 (2020).
\bibitem{bignell4} R.~Bignell, W.~Kamleh, and D.~Leinweber, EPJ WEb Conf. {\bf{245}}, 06033 (2020).

\bibitem{lensky} V.~Lensky, J.~McGovern, and V.~Pascalutsa, Eur.~Phys.J.~C {\bf{75}}, 604 (2015).
\bibitem{griesshammer} H.~Griesshammer, J.~McGovern, and D.~R.Phillips, Eur.~Phys.~J.~A {\bf{52}}, 139 (2016).
\bibitem{jwlee1} J.-W.~Lee and B.~Tiburzi, Phys.~Rev.~D {\bf{89}}, 054017 (2014).
\bibitem{jwlee2} J.-W.~Lee and B.~Tiburzi, Phys.~Rev.~D {\bf{90}}, 074036 (2014).
\bibitem{wilcox1} W.~Wilcox, Ann. Phys. {\bf{255}}, 60 (1997).
\bibitem{wilcox2} W.~Wilcox, Phys. Rev D {\bf{57}}, 6731 (1998).
\bibitem{christensen} F.~X.~Lee, W.~Wilcox, L.~Zhou, Nucl. Phys.~Proc.~Suppl. {\bf{119}}, 269 (2003).

\bibitem{zhou} L.~Zhou, F.~X.~Lee, W.~Wilcox, J.~Christensen, Nucl. Phys. Porc. Suppl. {\bf{119}}, 272 (2003).
\bibitem{lee2} F.~X.~Lee, L.~Zhou, W.~Wilcox, J.~Christensen, PoS {\bf{LAT2005}}, 031 (2006).
\bibitem{MILC} C.~W. Bernard, T.~Burch, K.~Orginos, D.~Toussaint, T.~A.~DeGrand, C.~DeTar, S.~Datta,
S.~A.~Gottlieb, U.~M.~Heller adn R.~Sugar, Phys.~Tev.~\textbf{D 64} (2001) 054506.
\bibitem{foldy} L.~Foldy, Phys. Rev. Lett. {\bf 3}, 105 (1959).
\bibitem{engelhardt4} S.~N.~Syritsyn, J.~D.~Bratt, M.~F.~Lin, H.~B.~Meyer, J.~W.~Negele, A.~V.~Pochinsky, M.~Procura, M.~Engelhardt, Ph.~Hagler, T.~R.~Hemmert, W.~Schroers, Phys.~Rev.~D {\bf 81}, 034507 (2010).
\bibitem{PDG2017} C.~Patrignani et al. (Particle Data Group), Chin. Phys. C, {\bf 40}, 100001 (2016) and 2017 update.
\bibitem{bratt} J.~D.~Bratt, R.~G.~ Edwards, M.~Engelhardt, P.~Hagler, H.~W.~Lin, M.~F.~Lin, H.~B.~Meyer, B.~Musch, J.~W.~Negele, K.~Orginos, A.~V.~Pochinsky, M.~Procura, D.~G.~Richards, W.~Schroers, S.~N.~Syritsin, Phys. Rev. D {\bf 82}, 094502 (2010).
\bibitem{excited} J.R.~Green, M.~Engelhardt, N.~Hasan, S.~Krieg, S.~Meinel, 
J.W.~Negele, A.V.~Pochinsky, S.N.~Syritsyn, Phys.~Rev.~D {\bf{100}}, 074510 (2019).

\end{thebibliography}

\section*{Appendix}
\input{appendix.tex}


